Fixing Vulnerabilities Hinders Maintainability

### 2019-02-05 paper/ICPC19/icpc19.tex
icp19

>>>>

We measured the effect sizes between both distribution - before and after patches - per 
language and security flaw using the Common Language Effect Size~\cite{cliff:1993} method
to understand the magnitude of the differences between distributions. Overall, the effect 
sizes were of a low-medium level. Thus, considering the median equal 0 and the low size effects
it is reasonable to affirm that there is a significant real effect but it might only be 
recognized after a thoughtful data analysis.
